\subsection{c}
If limited to sampling $n+1$ price points for $\{X_t\}$, (including $X_0$ and $X_T$) prove that
\begin{itemize}
	\item For estimating $\sigma^2$, sampling, the ML estimators vary with the increment spacing, but the variance of these estimators are all equal, regardless of the increment spacing.
	\item For estimating $\mu$, all ML estimators are the same and have the same variance, regardless of the increment spacing.
\end{itemize}

\begin{solution}
Finding answer for $\sigma^2$ estimator.

We can see from derivation of ML estimate of that for $n+1$ in \ref{subsection_2_b} 
spaced over period T we have to decide first how to assign weight $g_0$ to r.v $Y_0$ and modify weights $h_i$ for subsequent
samples. One scheme could be:

\begin{equation}
g_i = \left\{ 
\begin{aligned}
\frac{h_1}{2} \quad& for \quad i = 0 \\
\frac{h_i + h_{i+1}}{2} \quad& for \quad i = 1 \ldots (n-1) \\
\frac{h_n}{2} \quad& for \quad i = n 
\end{aligned}\right.
\end{equation}

Using above we can re-write formula for $\hat{\sigma}^2$:

\begin{equation}
\begin{aligned}
\hat{\sigma}^2  &= \frac{1}{n+1}\left[\frac{(Y_0-\hat{\mu} \frac{h_1}{2})^2}{\frac{h_1}{2}} 
												+ \sum_{i=1}^{n-1}\frac{(Y_i-\hat{\mu}\frac{h_i + h_{i+1}}{2})^2}{\frac{h_i + h_{i+1}}{2}}
												+ \frac{(Y_n-\hat{\mu} \frac{h_n}{2})^2}{\frac{h_1}{2}}\right] \\
								&= \frac{1}{n+1}\sum_{i=0}^{n}\frac{(Y_i-\hat{\mu} g_i)^2}{g_i}			
\end{aligned}
\end{equation}

where : $\sum_{i=0}^ng_i = T$.

From derivation in \ref{sigma_hat_distribution_3}\ref{eq:ap_sigma_square_expansion_2} we can see that: 

\begin{equation}
\begin{aligned}
(n+1)\hat{\sigma}^2 & = \sum_{i=0}^n\frac{(Y_i - \mu g_i)^2}{g_i} -T(\hat{\mu} - \mu)^2 \\
										& = \sum_{i=0}^n\frac{Y_i^2}{g_i} -2\mu\sum_{i=0}^nY_i + T\mu^2 -T(\hat{\mu} - \mu)^2 \\
										& = \sum_{i=0}^n\frac{Y_i^2}{g_i} -T\hat{\mu}^2
\end{aligned}
\end{equation}

Let's chose different set of sampling points $k_1 \ldots k_{n-1}$. We can see that the estimate formula will be different for each choice of intervals:

\begin{equation}
\hat{\sigma}_g^2 = \sum_{i=0}^{n}\frac{(Y_i-\mu g_i)^2}{g_i} \neq \hat{\sigma}_k^2 =\sum_{i=0}^{n}\frac{(Z_i-\mu k_i)^2}{k_i}			
\end{equation}

However both for the different choice of sampling intervals 
$\frac{(n+1)\hat{\sigma}_g^2}{\sigma^2} \thicksim \frac{(n+1)\hat{\sigma}_k^2}{\sigma^2} \thicksim \chi^2_{n}$, 
and variance of both estimators will be the same. $\square$

\end{solution}

\begin{solution}
Finding answer for $\mu$ estimator.

For $\hat{\mu} = $ estimator the ML formula for estimator doesn't depend on choice of sampling intervals. 
For any choice of intervals the ML estimate will result in the same formula, and having the same distribution. $\square$
\end{solution}